Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Most of the last proof done.

\begin{lemma}[Subject Reduction]
  \label{lem:subj_red}
  Let $e \to e'$.  Assume $\typeRule{pc}{e}{t}$ and $pc \in H$ for all $i \in
  \{1, 2\}$.  Then $\typeRule{pc}{e'}{t}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $e \to e'$.
  \begin{case}[$\beta$]
    \todo{}
  \end{case}

@@

  \begin{case}[let]
    \todo{}
  \end{case}

  \begin{case}[lift-app]
    \todo{}
  \end{case}

@@

  \begin{case}[bracket]
    \todo{}
  \end{case}
\end{proof}

>>>>

\begin{lemma}[Subject Reduction]
  \label{lem:subj_red}
  Let $e \to e'$.  Assume $\typeRule{pc}{e}{t}$ and $pc \in H$ for all $i \in
  \{1, 2\}$.  Then $\typeRule{pc}{e'}{t}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $e \to e'$.
  \begin{case}[$\beta$]
    In this case, $e = (\textsf{fix} f . \lambda x . e_0) v$.  In the premises
    of \textsc{E-App}, we have $\typeRule{ }{\textsf{fix} f . \lambda x .
    e_0}{(t' \to t)^l}$ and $\typeRule{ }{v}{t'}$.  The derivation of the
    function's type must end with \textsc{V-Abs} followed by some number of
    applications of \textsc{V-Sub}.  Applying Lemma~\ref{lem:weakening} and
    \textsc{E-Sub} to \text{V-Abs}'s premise gives $\typeRule{pc, (x \mapsto
    t''; f \mapsto \theta)}{e'}{t}$ for some $t''$ and $\theta$ which are
    subtypes of the function's type and the argument's type.  By \textsc{V-Sub},
    $\typeRule{ }{v}{t''}$ and $\typeRule{ }{\textsc{fix} f . \lambda x .
    e_0}{\theta}$.  Applying Lemma~\ref{lem:substitution} then gives
    $\typeRule{pc}{e'}{t}$.
  \end{case}

@@

  \begin{case}[let]
    By \textsc{E-Let} and Lemma~\ref{lem:substitution}.
  \end{case}

  \begin{case}[lift-app]
    $e = <v_1 | v_2> v$ in this case.  Then \textsc{E-App}'s premises are
    $\typeRule{ }{<v_1 | v_2>}{(t' \to t)^l}$, $\typeRule{ }{v}{t'}$, and $l
    \guards t$.  Lemma~\ref{lem:projection} gives $\typeRule{ }{v_i}{(t' \to
    t)^l}$ and $\typeRule{ }{\lift{v}_i}{t'}$ for $i \in \{1, 2\}$.  Applying
    \textsc{E-App} gives $\typeRule{pc \sqcup l}{v_i\lift{v}_i}{t}$.  Applying
    Lemma~\ref{lem:guard} gives $l \in H$.  Since we have $l \guards t$, we can
    apply \textsc{E-Bracket} to get $\typeRule{ }{e'}{t}$.
  \end{case}

@@

  \begin{case}[bracket]
    In this case $e = <e_1 | e_2>$, and $e'$ is the result of taking a step in
    one side of the brackets.  $e$'s typing derivation must end with
    \textsc{E-Bracket}, which has premises $\typeRule{pc \sqcup pc'}{e_i}{t}$,
    $\typeRule{pc \sqcup pc'}{e_j}{t}$, $pc' \guards t$, and $pc' \in H$.  Since
    $pc' \in H$, we can apply the inductive hypothesis to get $\typeRule{pc
    \sqcup pc'}{e_i'}{t}$ and $\typeRule{pc \sqcup pc'}{e_j'}{t}$.  The result
    is then given by applying \textsc{E-Bracket}.
  \end{case}
\end{proof}
